Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-09-23 writeup/rocha_etal.tex
Fix typo

\begin{abstract}
    The vigorous seasonal cycle of mixed layer modulates upper-ocean submesoscale turbulence.
    Here we provide model evidence that the seasonally-changing upper-ocean
    stratification also modulates submesoscale  (here 10-100 km)
    inertia-gravity waves. Summertime re-stratification weakens submesoscale
    turbulence but enhances inertia-gravity waves near the surface. Thus,
    submesoscale turbulence and inertia-gravity waves undergo vigorous out-of-phase
    seasonal cycles. These results imply a strong seasonal modulation of
    the skill and accuracy of geostrophic velocity diagnosed from submesoscale
    sea-surface height delivered by the Surface and Water Ocean Topography (SWOT)
    satellite mission
\end{abstract}

>>>>

\begin{abstract}
    The vigorous seasonal cycle of the mixed layer modulates upper-ocean submesoscale turbulence.
    Here we provide model evidence that the seasonally-changing upper-ocean
    stratification in the Kuroshio Extension also modulates submesoscale  (here 10-100 km)
    inertia-gravity waves. Summertime re-stratification weakens submesoscale
    turbulence but enhances inertia-gravity waves near the surface. Thus,
    submesoscale turbulence and inertia-gravity waves undergo vigorous out-of-phase
    seasonal cycles. These results imply a strong seasonal modulation of
    the skill and accuracy of geostrophic velocity diagnosed from submesoscale
    sea-surface height delivered by the Surface and Water Ocean Topography (SWOT)
    satellite mission
\end{abstract}
